\chapter{Introduction}
%  motivacao
%  objetivos
%  organizacao
The remainder of this paper is organized as follows:
section 2 gives details on preliminary searches, explaining why the field of sequence learning was elected as the focus of this study, section 3 describes the search process and execution, section 4 discusses the results found and section 5 comments on the planning of further research based on the answered questions.


\chapter{File deletion and recovering}
% o que acontece quando um arquivo é deletado
%   Exemplo de arquivo em um sistema de arquivos NTFS
%     MFT
%       directory entry
%       file entry
%       entry pointing to position in disk
%         comment append, fragmentation and slack
%       file deletion
% recover strategies
%  using MFT data
%  find lost MFT data
%  data-carving

\chapter{Data-carving}
% desafios do data-carving
%  fragmentacao
%  reconhecimento de estruturas
% solucoes existentes
%  abordagens comuns
%   magic numbers
%   skip known files
%   use content to infer file size
%   use fixed value as file size
%   watch content to infer when file ended
%   test opening the file
% exemplo de arquivo 
Data carving is a forensic process that attempts to recover files without previous information of where the file starts or ends.
To accomplish this, a software has to analyze a source of raw data, searching for patterns indicating a know file type and making attempts to locate and reconstruct each of its constituent parts.
That process commonly disregards the filesystem, being able to recover deleted files from unallocated areas, but faces the problem of fragmentation: in many cases, files are not written sequentially on disk and deleted files may have missing parts.

For example, while doing data carving on a hard drive, a software could sequentially read each drive sector, find a known header of a video file and save the following sectors until a footer is found or a size limit is reached. This is a common data carving approach, but one that fails to recover fragmented videos.

The patterns searched by data carving software are generally manually coded, taking advantage of fixed byte sequences found on headers and footers. But the amount of different file types combined with the slow process of manually coding each of those patterns makes the development of data carving software a tedious task.

The application of machine learning solutions to this manual task has the potential to make it easier and faster. An initial strategy could be to train a classifier to, given a chunk of data, provide a label indicating a file type. That could be used to recover unfragmented deleted files.

The recovery of fragmented files through data carving would require some sort of pattern recognition on the identified chunks, in order to reconstruct the correct sequence.

This systematic mapping study objective is to identify some of the potential machine learning approaches that could be used to automate the construction of data carving software.

\chapter{Machine learning}

\chapter{Proposal}

\chapter{Schedule}
